---
title: "Project1"
output:
  html_document: default
  pdf_document: default
date: "2023-09-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r}
library(here)
library(tidyverse)
```


```{r}
library(gapminder)
library(dplyr)

# tests if a directory named "data" exists locally
if (!dir.exists(here("data"))) {
  dir.create(here("data"))
}

# saves data only once (not each time you knit a R Markdown)
if (!file.exists(here("data", "chocolate.RDS"))) {
  url_csv <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv"
  chocolate <- readr::read_csv(url_csv)
  
  # save the file to RDS objects
  saveRDS(chocolate, file = here("data", "chocolate.RDS"))
}

chocolate <- readRDS(here("data", "chocolate.RDS"))
as_tibble(chocolate)
```


```{r}
glimpse(chocolate)
```
### Part1 {.tabset .tabset-fade}
#### Question1
I think setting the number of bins tobe 15 is the most appropriate. When the number is 15, there is few empty slots in the histogram and we can easily see the distribution.
```{r}
qplot(rating, data=chocolate)
qplot(rating, data=chocolate, bins=10)
qplot(rating, data=chocolate, bins=15)
qplot(rating, data=chocolate, bins=20)
qplot(rating, data=chocolate, bins=25)
```

#### Question2
```{r}
library(dplyr)

reviews_by_country <- chocolate %>%
  group_by(country_of_bean_origin) %>%
  summarise(count = n())
print(reviews_by_country)
```

#### Question3
```{r}
ecuador_chocolates <- chocolate %>%
  filter(country_of_bean_origin == "Ecuador")
mean <- mean(ecuador_chocolates$rating)
total <- sum(!is.na(ecuador_chocolates$rating))
sd <- sd(ecuador_chocolates$rating)
print(mean)
print(total)
print(sd)
```

#### Question4
```{r}
best_ecuador_chocolate <- ecuador_chocolates %>%
  group_by(company_manufacturer) %>%
  summarise(average_rating = mean(rating, na.rm = TRUE))
best_company <- best_ecuador_chocolate %>%
  filter(average_rating == max(average_rating))
print(best_company[,1])
```

#### Question5
```{r}
average_ratings_by_country <- chocolate %>%
  group_by(country_of_bean_origin) %>%
  summarise(average_rating = mean(rating, na.rm = TRUE))
sorted_countries <- average_ratings_by_country %>%
  arrange(desc(average_rating))
top_3_countries <- head(sorted_countries, n = 3)
print(top_3_countries[,1])
```

#### Question6
```{r}
average_ratings_by_country <- chocolate %>%
  group_by(country_of_bean_origin) %>%
  summarise(average_rating = mean(rating, na.rm = TRUE), review_num = n())
more_10_countries <- average_ratings_by_country %>% filter(review_num >= 10)
sorted_countries <- more_10_countries %>% arrange(desc(average_rating))
top_3_countries <- head(sorted_countries, n = 3)
print(top_3_countries[,1])
```

#### Question7
```{r}
#Identify the countries of bean origin with at least 50 reviews
reviews_by_country <- chocolate %>%
  group_by(country_of_bean_origin) %>%
  summarise(review_count = n())
countries_with_50_reviews <- reviews_by_country %>%
  filter(review_count >= 50) %>%
  pull(country_of_bean_origin)
filtered_chocolate <- chocolate %>%
  filter(country_of_bean_origin %in% countries_with_50_reviews)

#create a new column that groups chocolate percentages into one of four groups
filtered_chocolate_percent <- filtered_chocolate %>%
  mutate(chocolate_percentage_group = case_when(
    substr(cocoa_percent, 1, 2) < 60 ~ "<60%",
    substr(cocoa_percent, 1, 2) >= 60 & substr(cocoa_percent, 1, 2) < 70 ~ "60% to 70%",
    substr(cocoa_percent, 1, 2) >= 70 & substr(cocoa_percent, 1, 2) < 90 ~ "70% to 90%",
    substr(cocoa_percent, 1, 2) >= 90 ~ ">=90%"
  ))
head(filtered_chocolate_percent)
```


```{r}
options(repr.plot.width = 12, repr.plot.height = 9)
boxplot_plots <- 
  ggplot(filtered_chocolate_percent, aes(x = chocolate_percentage_group, y = rating)) +
  geom_boxplot() +
  facet_wrap(~ country_of_bean_origin) +
  labs(title = "Ratings by Chocolate Percentage Group",
       x = "Chocolate Percentage Group",
       y = "Rating") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

print(boxplot_plots)
```

### Part2 {.tabset .tabset-fade}
```{r}
library(gapminder)
head(gapminder)
```

#### Question1
```{r}
library(dplyr)
lookup_table <- gapminder %>%
  
  select(country, continent) %>%
  distinct()

chocolate %>%
  select(country_of_bean_origin) %>%
  distinct()

chocolate_continent <- chocolate %>%
  mutate(country_of_bean_origin = ifelse(country_of_bean_origin == "U.S.A.", "United States", country_of_bean_origin)) %>% 
  mutate(country_of_bean_origin = ifelse(country_of_bean_origin %in% c("Sao Tome", "Principe", "Sao Tome & Principe"), "Sao Tome and Principe", country_of_bean_origin)) %>% 
  mutate(country_of_bean_origin = ifelse(country_of_bean_origin == "DR Congo", "Congo, Dem. Rep.", country_of_bean_origin)) %>% 
  left_join(lookup_table, by = c("country_of_bean_origin" = "country"))
#head(chocolate_continent)

chocolate_continent %>% 
  distinct(continent)

chocolate_continent %>% 
  filter(is.na(continent)) %>% 
  distinct(country_of_bean_origin)
# 24 countries are with NA values


chocolate_continent <- chocolate_continent %>%
  mutate(continent = as.character(continent)) %>% 
  mutate(continent = ifelse(country_of_bean_origin %in% c("Fiji", "Papua New Guinea", "Vanuatu", "Solomon Islands", "Samoa"), "Oceania", continent)) %>% 
  mutate(continent = ifelse(country_of_bean_origin %in% c("Belize", "Grenada", "Martinique", "St. Lucia", "St.Vincent-Grenadines", "Suriname","Tobago","Trinidad"), "Americas", continent)) %>%
  mutate(continent = ifelse(country_of_bean_origin %in% c("Burma", "Sumatra", "Sulawesi"), "Asia", continent)) %>%
  mutate(continent = ifelse(country_of_bean_origin %in% c("Ivory Coast","Congo"), "Africa", continent))


  
```

#### Question2
```{r}
filtered_chocolate_continent <- chocolate_continent %>%
   inner_join(more_10_countries, by = "country_of_bean_origin")
 
 head(filtered_chocolate_continent)
 
 chocolate_continent %>% 
   distinct(continent)
```

#### Question3
```{r}
filtered_chocolate_continent <- filtered_chocolate_continent %>%
  filter(country_of_bean_origin != "Blend")

# View the updated dataset
head(filtered_chocolate_continent)
```

#### Question4
```{r}
#filtered_chocolate_continent <- #filtered_chocolate_continent[!is.na(filtered_chocolate_continent$continent), ]
violin_plots <- ggplot(filtered_chocolate_continent, 
                       aes(x = continent, y = average_rating)) +
  geom_violin() +
  labs(title = "Ratings by Continent",
       x = "Continent",
       y = "Rating") +
  theme_minimal()

chocolate_continent %>% 
  distinct(continent)

print(violin_plots)
```

### Part3 {.tabset .tabset-fade}
#### Question1
```{r}
library(tidyr)
library(dplyr)
chocolate_with_ingredients <- chocolate %>%
  mutate(
    beans = ifelse(grepl("B", ingredients), 1, 0),
    sugar = ifelse(grepl("S" , ingredients), 1, 0),
    cocoa_butter = ifelse(grepl("C" , ingredients), 1, 0),
    vanilla = ifelse(grepl("V" , ingredients), 1, 0),
    lecithin = ifelse(grepl("L" , ingredients), 1, 0),
    salt = ifelse(grepl("Sa" , ingredients), 1, 0)
  )

head(chocolate_with_ingredients)
```

#### Question2
```{r}
chocolate_with_ingredients_char <- chocolate_with_ingredients %>%
  mutate(
    char_cocoa = ifelse(grepl("cocoa", most_memorable_characteristics), 1, 0),
    char_sweet = ifelse(grepl("sweet", most_memorable_characteristics), 1, 0),
    char_nutty = ifelse(grepl("nutty", most_memorable_characteristics), 1, 0),
    char_creamy = ifelse(grepl("creamy", most_memorable_characteristics), 1, 0),
    char_roasty = ifelse(grepl("roasty", most_memorable_characteristics), 1, 0),
    char_earthy = ifelse(grepl("earthy", most_memorable_characteristics), 1, 0)
  )
head(chocolate_with_ingredients_char)
```

#### Question3
```{r}
means_by_year <- chocolate_with_ingredients_char %>%
  group_by(review_date) %>%
  summarise(
    mean_char_cocoa = mean(char_cocoa),
    mean_char_sweet = mean(char_sweet),
    mean_char_nutty = mean(char_nutty),
    mean_char_creamy = mean(char_creamy),
    mean_char_roasty = mean(char_roasty),
    mean_char_earthy = mean(char_earthy),
    mean_beans = mean(beans),
    mean_sugar = mean(sugar),
    mean_cocoa_butter = mean(cocoa_butter),
    mean_vanilla = mean(vanilla),
    mean_lecithin = mean(lecithin),
    mean_salt = mean(salt)
  )

means_by_year
```

#### Question4
```{r}
library(tidyr)

long_means_by_year <- means_by_year %>%
  pivot_longer(
    cols = starts_with("mean_"),
    names_to = "feature",
    values_to = "mean_score")
head(long_means_by_year)
```

### Part 4 
```{r}
plot_list <- list()

features <- c("char_cocoa", "char_sweet", "char_nutty", "char_creamy", "char_roasty", "char_earthy", "beans", "sugar", "cocoa_butter", "vanilla", "lecithin", "salt")

for (feature in features) {
  p <- ggplot(long_means_by_year, aes(x = review_date, y = mean_score)) +
    geom_point() +
    geom_smooth(method = "loess", se = FALSE) +
    labs(
      title = paste("Trend in Mean Score for", feature),
      subtitle = "Key trends summary",
      x = "Year",
      y = "Mean Score"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 5),    
      plot.subtitle = element_text(size = 4),  
      axis.title.x = element_text(size = 4),  
      axis.title.y = element_text(size = 4),   
      axis.text.x = element_text(size = 4),    
      axis.text.y = element_text(size = 4)  
    )
  
  p <- p + coord_cartesian(ylim = c(0, 1)) +
    theme(
      plot.background = element_blank(),
      panel.border = element_rect(fill = NA, color = "black"),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      plot.margin = margin(1, 1, 1, 1, "cm")
    ) +
    theme(
      plot.margin = margin(0.01,0.01,0.01,0.01, "in"),
      plot.title = element_text(hjust = 0.5),
      plot.caption = element_text(hjust = 0.5)
    ) +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.text.y = element_text(angle = 0, hjust = 1)
    )
  
  plot_list[[feature]] <- p
}

library(patchwork)
wrap_plots(plot_list, nrow = 5)
```

### Part 5 {.tabset .tabset-fade}
```{r}
chocolate %>% 
  ggplot(aes(x = country_of_bean_origin, y = rating, color = company_location))+
  # x represent country of bean origin which has too many unique values
  # y represent ratings which are same for many row, points stacked on top of each other
  # color the points by the company location makes the plot much more messy and hard to derive information
  geom_point(alpha = 0.1, shape = 18, size = 6)+
  # geom_point is not a good choice, should consider violin/boxplot in this case
  # size of the points is too big
  # alpha controls the transparency of the points, which is too high
  # shape = 18 changes the shape of point from circle to diamond shape
  theme(legend.position = "none",
        panel.background = element_rect(fill = "pink"))
  # legend is hided with no equivalent information in the plot
  # change the background color to pink, which is very similar to point color
  
```

### Part 6 {.tabset .tabset-fade}
```{r}
chocolate %>%
  ggplot(aes(
      x = as.factor(review_date),
      y = rating,
      fill = review_date
  )) +
  # Here I adjust the width and the position of the plots
  geom_violin(width = 0.7, position = position_nudge(x = 0.15)) +
  # Here I change the fill and border colors of the violin plots
  geom_violin(fill = "skyblue", color = "darkblue")+
  # Here I add a box plot inside the violin plot to provide additional summary statistics for the distribution
  geom_boxplot(width = 0.1, fill = "white", color = "black")+
  # Here I add the table and axis label to make the graph easier to understand. 
  labs(
    title = "Distribution of Ratings by Year",
    x = "Year",
    y = "Rating",
    fill = "Year") +
  # Here I adjust to my favorite theme
  theme_minimal() +
  # Here I rotate the x-axis label to make it clearer
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # Here I add a new legend for better understanding.
  guides(fill = guide_legend(title = "Year"))


```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
